---
title: "Comparing depression stressors between demographic groups"
output:
  pdf_document: default
  html_notebook: default
---



```{r}

library(jsonlite)
library(stm)
library(quanteda)
library(spacyr)
library(stringr)
library(wordcloud)
library(ggplot2)
```
# Cleaning up gender/COVID-19 labels


```{r}
gender_func <- function(gender_label){
  if(gender_label == "woman"){
    return("Female")
  } else if(gender_label == "man") {
    return("Male")
  } else {
    return("other")
  }
}

covid_func <- function(covid_label){
  if(covid_label == 2020 || covid_label == 2021 ){
    return(TRUE)
  } else{
    return(FALSE)
  }
}
```

```{r}
survey_meta <- read.csv("/Users/shinkamori/Documents/Research/non_covid_and_covid.csv")
survey_meta$gender <- sapply(survey_meta$gender, gender_func)
survey_meta$pandemic <- sapply(survey_meta$Year, covid_func)
```

```{r}
summary((survey_meta))
```
# Preprocessing the data
- stemming, lowercase, remove punctuation and stopwords
- `meta` = metadata(gender, race, pandemic)


```{r}
processed <- textProcessor(survey_meta$text, metadata=survey_meta[, c( "gender", "race", "pandemic")])
out <- prepDocuments(processed$documents, processed$vocab, processed$meta)
```
```{r}
temp_text <- survey_meta[-processed$docs.removed,]

```

# Fitting model
We use 25 topics(`K = 25`) with the covariates gender, race and pandemic


```{r}
model_depression <- stm::stm(
  documents = out$documents,
  K = 25,
  prevalence =~ gender + race + pandemic,
  data=out$meta,
  vocab = out$vocab,
  max.em.its=75
)

```

Printing out the most likely top-30 keywords per topic

```{r}
labelTopics(model_depression, n = 30)

```
Initial labels before removing unclear topics


```{r}
# topic_list = c(
#   "daily stress", "health issues", "family hardships", "serious health issues", 
#   "work", "news and social media", 
#   "relationships",  "school", "school", "unemployment/loss", "relationships","finances"
# )
topic_list = c("feeling stuck", "staying strong", "comparing to others", "work1", "mental health", "uncertainty", "finances/unemployment", "pandemic", "helplessness", "police brutality", "stress and anxiety", "news", "school", "racism", "police brutality", "homesick", "supporting family", "politics", "family", "Loneliness", "(21)", "relationships", "perfectionism", "(24)", "work2")
```

Getting `estimateEffects` to get the effect of gender, race and pandemic on the distribution of the topic content

```{r}
prep_gender <- stm::estimateEffect(~ gender, 
                                   model_depression,
                                   meta = survey_meta[, c( "gender", "race", "pandemic")], uncertainty = "Global")

prep_eth <- stm::estimateEffect(~ race,
                                model_depression,
                                meta = survey_meta[, c( "gender", "race",  "pandemic")], uncertainty = "Global")
prep_pan <- stm::estimateEffect(~ pandemic, 
                                model_depression,
                                meta = survey_meta[, c( "gender", "race",  "pandemic")], uncertainty = "Global")
```

Finalizing the topic list and removing unclear otpics

```{r}
# topic_list = c(
#   "daily stress", "health issues", "family hardships", "serious health issues", 
#   "work", "news and social media", 
#   "relationships",  "school", "school", "unemployment/loss", "relationships","finances"
# )
# topic_list = c("--", "--", "--", "work1", "health", "--", "finances", "---", "---", "---", "---", "news and socia media", "school", "---", "---", "---", "---", "news and politics", "family", "---", "---", "relationships", "---", "---", "work2")
topic_list = c( "work-fatigue", "health", "finances and unemployment", "stress", "news and social media", "school", "news and politics", "family",  "relationships", "work-pressure")
topicss = c(4,5,7,11,12,13,18,19,22,25)
```

# Results
Here we show the pairwise comparison for each demographic group using the result of `estimateEffects`.

```{r}
make_plot <- function(param, range_val, title, positive_color, negative_color, label1, label2,  arrow_length=0.03, text_offset=2){
means <- param$means
topics <- param$topics
topic <- c(1:length(gender$topics))
cis <- param$cis
labels <- param$labels
# Plot
plot_data <- data.frame(topics = topics, means = unlist(means), lower = sapply(cis, "[[", 1), upper = sapply(cis, "[[", 2))
ylim_range <- range(plot_data$lower, plot_data$upper)
ylim_range[2] <- ylim_range[2] + 0.01
# Create the plot with mean on the x-axis
plot(plot_data$means, plot_data$topics, type = "n", ylab = "", , yaxt = "n", xlab =title,
     xlim = range_val, ylim = c(0, length(topics)+2))

# Add dotted line at x = 0
abline(v = 0, lty = 2)
    it <- length(topics)
    for(i in 1:length(topics)){
      if(means[[i]] >= 0) {
        color = positive_color
      } else {
        color = negative_color
      }
      points(means[[i]], it, pch=16, col = color)
      lines(c(cis[[i]][1],cis[[i]][2]),c(it,it), col = color, lwd=2)
      # axis(2,at=it, labels=stringr::str_wrap(labels[i],width=width),las=1, cex=.25, tick=F, pos=cis[[i]][1])
      text(means[[i]], it, labels[[i]], pos = 2, offset = text_offset, cex=1.05 )
      it = it-1
    }

  arrow_x <-range_val[1] + arrow_length
  # arrow_y <- mean(topics)
  Y = length(topics) 
  # Add arrow
  arrows(range_val[1] + 2*arrow_length, Y+1, range_val[1], Y+1, length = 0.1, col = negative_color, lwd = 2)#left-neg
  
  arrows(range_val[2] - 2*arrow_length, Y+1,  range_val[2], Y+1, length = 0.1, col = positive_color, lwd = 2)#right-pos
  
  X1 = (0.01+range_val[1] + 2*arrow_length + range_val[1])/2
  X2 = (range_val[2] - 2*arrow_length + range_val[2]-0.01)/2
  text(X1, Y+1.8, label1, cex = 1)
  text(X2, Y+1.8, label2, cex = 1)
}
```

Assigning colors to categories

```{r}
white <- "red"
asian <- "magenta2"
black <- "green3"
hispanic <- "blue"
men <- "darkorchid"
women <- "orangered"
```




```{r}

gender <- plot(prep_gender, covariate = "gender", model = model_depression, method = "difference", 
     cov.value1 = "Male", cov.value2 = "Female",
     xlab = "More Female ... More Male",
     labeltype = "custom",
     custom.labels = topic_list,
     xlim = c(-0.05, 0.05),
     main = "Effect of Gender",
    topics =topicss
)
```
# Topics matching with UMD-ODH
Here we plot only topics that have a match with topic in UMD-ODH

## Gender
Topics on the left implies it is more prevalent for female, topic on the right implies it is more prevalent for male. Color coded by dempgraphic.
```{r}
make_plot(gender, range(-0.04, 0.04),  "",men, women, "More Female", "More Male",  0.01, 4)

```




```{r}
w_b <- plot(prep_eth, covariate = "race", model = model_depression, method = "difference", 
     cov.value1 = "white", cov.value2 = "black",
     xlab = "More African American ... More White",
     labeltype = "custom",
     custom.labels = topic_list,
     xlim = c(-0.15, 0.15),
       topics = topicss
     )
w_a <- plot(prep_eth, covariate = "race", model = model_depression, method = "difference", 
     cov.value1 = "white", cov.value2 = "asian",
     xlab = "More Asian ... More White",
     labeltype = "custom",

     custom.labels = topic_list,
     xlim = c(-0.15, 0.15),
       topics = topicss
     )
w_h <- plot(prep_eth, covariate = "race", model = model_depression, method = "difference", 
     cov.value1 = "white", cov.value2 = "hispanic",
     xlab = "More Hispanic ... More White",
     labeltype = "custom",

     custom.labels = topic_list,
     xlim = c(-0.15, 0.15),
       topics = topicss
     )
```
## Race
### White vs. Other

We plot comparisons of the White group to all other groups

```{r}
range_val <- range(-0.15, 0.15)
make_plot(w_b, range_val,  "", white, black, "More African American", "More White")
make_plot(w_a, range_val,  "",white, asian, "More Asian", "More White")
make_plot(w_h, range_val,  "",white, hispanic, "More Hispanic", "More White")

```

### Asian vs. African Americam
```{r}
b_a <- plot(prep_eth, covariate = "race", model = model_depression, method = "difference", 
     cov.value1 = "black", cov.value2 = "asian",
     xlab = "More Asian ... More African American",
     labeltype = "custom",
     custom.labels = topic_list,
     xlim = c(-0.15, 0.15),
     topics = topicss
     )
make_plot(b_a, range_val,  "", black, asian, "More Asian", "More African American")

```
## Hispanic vs. Asian
```{r}
h_a <- plot(prep_eth, covariate = "race", model = model_depression, method = "difference", 
     cov.value1 = "hispanic", cov.value2 = "asian",
     xlab = "More Asian ... More Hispanic",
     labeltype = "custom",
     custom.labels = topic_list,
     xlim = c(-0.15, 0.15),
     topics = topicss
     )
make_plot(h_a, range_val,  "",hispanic, asian,  "More Asian", "More Hispanic")
```
## Hispanic vs. African American

```{r}
b_h <- plot(prep_eth, covariate = "race", model = model_depression, method = "difference", 
     cov.value1 = "black", cov.value2 = "hispanic",
     xlab = "More Hispanic ... More African American",
     labeltype = "custom",
     custom.labels = topic_list,
      xlim = c(-0.2, 0.2),
     topics = topicss

     )
make_plot(b_h, range_val,  "",black, hispanic,  "More Hispanic", "More African American")

```
### 
```{r}
# topic_list = c(
#   "daily stress", "health issues", "family hardships", "serious health issues", 
#   "work", "news and social media", 
#   "relationships",  "school", "school", "unemployment/loss", "relationships","finances"
# )
# topic_list = c("--", "--", "--", "work1", "health", "--", "finances", "---", "---", "---", "---", "news and socia media", "school", "---", "---", "---", "---", "news and politics", "family", "---", "---", "relationships", "---", "---", "work2")
topic_list = c( "work1", "health", "finances and unemployment", "news and social media", "school", "news and politics", "family",  "relationships", "work2")
# topic_idx = c(4,5)

topic_list = c("feeling stuck", "staying strong", "comparing to others", "uncertainty",  "pandemic", "helplessness", "police violence", "stress and anxiety","racism", "police brutality", "immigration", "fear of deportation", "loneliness",  "perfectionism" )
topic_idx = c(1,2,3,6,8,9,10,11,14,15,16,17,20,23)
```

```{r}
w_b2 =plot(prep_eth, covariate = "race", model = model_depression, method = "difference", 
     cov.value1 = "white", cov.value2 = "black",
     xlab = "More African American ... More White",
     labeltype = "custom",
     custom.labels = topic_list,
     xlim = c(-0.15, 0.15),
       topics = topic_idx
     )
w_a2 = plot(prep_eth, covariate = "race", model = model_depression, method = "difference", 
     cov.value1 = "white", cov.value2 = "asian",
     xlab = "More Asian ... More White",
     labeltype = "custom",

     custom.labels = topic_list,
     xlim = c(-0.15, 0.15),
       topics = topic_idx
     )
w_h2 = plot(prep_eth, covariate = "race", model = model_depression, method = "difference", 
     cov.value1 = "white", cov.value2 = "hispanic",
     xlab = "More Hispanic ... More White",
     labeltype = "custom",

     custom.labels = topic_list,
     xlim = c(-0.15, 0.15),
       topics = topic_idx
     )
```
# All other topics
Here we plot topics that do not have a corresponding pair in UMD-ODH

```{r}
make_plot(w_b2, range_val,  "More African American vs. More White", white, black, "More African American", "More White")
make_plot(w_a2, range_val,  " More Asian vs. More White",white, asian, "More Asian", "More White", )
make_plot(w_h2, range_val,  " More Hispanic vs. More White",white, hispanic, "More Hispanic", "More White")
```
### Asian vs. African American

```{r}
a_b2 <- plot(prep_eth, covariate = "race", model = model_depression, method = "difference", 
     cov.value1 = "black", cov.value2 = "asian",
     xlab = "More Asian ... More African American",
     labeltype = "custom",
     custom.labels = topic_list,
     xlim = c(-0.15, 0.15),
    topics = topic_idx
     )
make_plot(a_b2, range_val,  " More Asian vs. More African American",black, asian, "More Asian", "More African American")

```
### Hispanics vs. Asian
```{r}
h_a2 <- plot(prep_eth, covariate = "race", model = model_depression, method = "difference", 
     cov.value1 = "hispanic", cov.value2 = "asian",
     xlab = "More Asian ... More Hispanic",
     labeltype = "custom",
     custom.labels = topic_list,
     xlim = c(-0.1, 0.1),
     topics = topic_idx
     )
make_plot(h_a2, range_val,  "More Asian vs. More Hispanic",hispanic, asian,  "More Asian", "More Hispanic")

```
### Hispanic vs. African American
```{r}
h_b2 <- plot(prep_eth, covariate = "race", model = model_depression, method = "difference", 
     cov.value1 = "black", cov.value2 = "hispanic",
     xlab = "More Hispanic ... More African American",
     labeltype = "custom",
     custom.labels = topic_list,
      xlim = c(-0.15, 0.15),
     topics = topic_idx

     )
make_plot(h_b2, range_val,  "More Hispanic vs. More African American",black, hispanic,  "More Hispanic", "More African American")

```
### Gender
```{r}

w_m2 <- plot(prep_gender, covariate = "gender", model = model_depression, method = "difference", 
     cov.value1 = "Male", cov.value2 = "Female",
     xlab = "More Female ... More Male",
     labeltype = "custom",
     custom.labels = topic_list,
     xlim = c(-0.05, 0.05),
     main = "Effect of Gender",
    topics = topic_idx
)
make_plot(w_m2,  range(-0.04, 0.04),  "More Female vs. More Male",men, women,   "More Female", "More Male",  0.01, 3.5)

    

```
```{r}
sample <- plot(prep_gender, covariate = "gender", model = model_depression, method = "difference", 
     cov.value1 = "Male", cov.value2 = "Female",
     xlab = "More Female ... More Male",
     labeltype = "custom",
     xlim = c(-0.05, 0.05),
     main = "Effect of Gender",
    topics = topic_idx
)
```






